Hierarchical Large Language Models for Multi-task problems

### 2024-03-11 paper/main.tex
Updates from Overleaf

\subsection{Low-Rank Adaption of Language Models}
Low-Rank Adaption (LoRA)

[This might be background?]
\begin{itemize}
    \item explain what pretraining LLM means
    \item Explain how LORA fine tuned is done on each task
    \item Explain how LORA finetuned also could be done on all tasks together if they have a similar data distribution.
\end{itemize}

@@

During LoRA fine-tuning, the low-rank factors $A$ and $B$ are learned as normal parameters, while the original pretrained weights $W_{full}$ are kept fixed.

@@

These datasets will have a shared domain (Norwegian) that is different from what the pretrained foundational model is trained on.
We use two tasks containing the same dataset distribution to see how sharing knowledge through the hierarchical prior can benefit datasets with few examples.

>>>>

\subsection{Finetuning methods}
Talk about alternative finetuning methods to lora: finetune top layer (traditional),

sira (\cite{zhu_sira_2023})

@@

During LoRA fine-tuning, the low-rank factors $A$ and $B$ are learned from data as normal parameter matricies, while the original pretrained weights $W_{full}$ are kept fixed.

@@

%\end{document}
